A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-10 paper/paper.tex
Pushing data

\title{Probabilistic Audio Localization in Wireless Acoustic Sensor Networks}

@@

\author{Alexander Wallar}

@@

@@

PCA: Principle Component Analysis, or PCA, transforms a set of variables in
their "principle components", or linearly uncorrelated variables.

@@

\cite{wallar2015reactive}

\begin{algorithm}[ht] 
    \caption{Multiple Source Sound Localization}
    \label{algo:MS}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $\Function{GetLocations}(\Var{r}, \Var{spl}, \Var{eventList}) \rightarrow$
        \STATE $\Var{locations} \leftarrow \Function{InitLocationList}()$
        \FORALL {$e \in \Var{eventList}$}
        \STATE $\Var{locations}.\Var{add}(\mathcal{L}_m(\Var{r}, \Var{spl}, \Var{eventList}, e.\Var{x}, e.\Var{y}))$
        \ENDFOR
        \STATE $\Var{centers} \leftarrow \Function{AffinityPropagation}(\Var{locations})$
        \COMMENT {\Var{centers} is a list of $(x, y, c)$ points where $c$ is the confidence}
        \RETURN $\Var{centers}$

>>>>

\title{A Comparison of Dimensionality Reduction Techniques for Robotic Motion
Planning}

@@

\author{Brandon Araki \and Alex Wallar}

@@

\newcommand{\xr}[0]{\ensuremath{{x_{\Var{rand}}}}}
\newcommand{\xnear}[0]{\ensuremath{{x_{\Var{near}}}}}
\newcommand{\xnearest}[0]{\ensuremath{{x_{\Var{nearest}}}}}
\newcommand{\xnew}[0]{\ensuremath{{x_{\Var{new}}}}}
\newcommand{\xmin}[0]{\ensuremath{{x_{\Var{min}}}}}
\newcommand{\cmin}[0]{\ensuremath{{c_{\Var{min}}}}}
\newcommand{\cost}[0]{\ensuremath{{\Function{Cost}}}}
\newcommand{\linef}[1]{\ensuremath{{c(\Function{Line}(#1))}}}

@@

PCA: Principle Component Analysis, or PCA, transforms a set of variables in
their "principle components", or linearly uncorrelated variables.\

@@

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}^*$~\cite{karaman2011sampling}}
    \label{algo:MS}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{Near}(G = (V, E), v,
            \gamma \cdot \Function{PRM}(\log(n) / n) ^ {1 / d})
            \backslash \{v\}$
            \FORALL{$u \in U$}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$

\begin{algorithm}[ht] 
    \caption{$\Function{RRT}^*$~\cite{karaman2011sampling}}
    \label{algo:MS}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\}$
        \STATE $E \leftarrow \emptyset$
        \FOR{$i = 1 \ \TO \ n$}
            \STATE $\xr \leftarrow \Var{SampleFree}_i$
            \STATE $\xnearest \leftarrow \Function{Nearest}(G = (V, E), \xr)$
            \STATE $\xnew \leftarrow \Function{Steer}(\xnearest, \xr)$
            \IF{$\Function{ObstacleFree}(\xnearest, \xnew)$}
                \STATE $\xnear \leftarrow \Function{Near}(G = (V, E), \xnew,
                \min \{\gamma \cdot \Function{RRT}(\log(|V|) / |V|)^{1 / d}, \eta\})$
                \STATE $V \leftarrow V \cup \{\xnew\}$
                \STATE $\xmin \leftarrow \xnearest$
                \STATE $\cmin \leftarrow \Function{Cost}(\xnear) +
                c(\Function{Line}(\xnearest, \xnew))$
                \FORALL{$\xnear \in X_{\Var{near}}$}
                    \STATE $C \leftarrow \cost(\xnear) + \linef{\xnear, \xnew}$
                    \IF{$\Function{CollisionFree}(\xnear, \xnew) \wedge C < \cmin$}
                        \STATE $\xmin \leftarrow \xnear$
                        \STATE $\cmin \leftarrow C$
                    \ENDIF
                    \STATE $E \leftarrow E \cup \{(\xmin, \xnew)\}$
                \ENDFOR
            \ENDIF
        \ENDFOR
        \RETURN $G = (V, E)$
